Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Clarify wording

It was shown that the peak torque coefficient computed this way shows similar
Reynolds number sensitivity, a better predictor than conventional
quantifications of airfoil performance, e.g., the lift-to-drag ratio. Note that this
method is not restricted to standard symmetrical NACA foils, though those
evaluated here with higher camber were more sensitive at lower $Re$, but had
smaller slopes in the linear~regime.

>>>>

It was shown that the peak torque coefficient computed this way shows similar
Reynolds number sensitivity as the experimental results for an actual turbine,
making it a better predictor than conventional quantifications of airfoil
performance, e.g., the lift-to-drag ratio. Note that this method is not
restricted to standard symmetrical NACA foils, though those evaluated here with
higher camber were more sensitive at lower $Re$, but had smaller slopes in the
linear~regime.
